### 2016-08-26 notions.tex
notes from phone call

In this experiment we track the time-complexity (relative to some
implied model of computation) and query-complexity (i.e., number of
queries) of the adversary~$A$.
We define the advantage of adversary~$A$ in the correctness experiment as
$\AdvCorrect{\Pi,\distr{}{},r}{A} = \Prob{\ExpCorrect{\Pi,\distr{}{}, r,}{A}=1}$.
Overloading notation, we write $\AdvCorrect{\Pi,\distr{}{},r}{t,q}$ for the maximum over all~$t$-time adversaries that ask at most~$q$ queries. Roughly, we say that a
set-representation~$\Pi$ is $(t,q,r,\epsilon')$-correct if $\AdvCorrect{\Pi,\distr{}{},r}{t,q} \leq \epsilon'$.

@@

\item If a scheme is $(t,q,1,\epsilon)$-correct, then it is also $\epsilon$-secure under the NY definition,
at least for attackers making at most $q-1$ queries.
This is immediate.
\end{enumerate}

@@

\jnote{OK, from here on I specialize to set-representation data structures\ldots}
The one-wayness definition (see
Figure~\ref{fig:privacy-ow}) is parameterized by a distribution $\distr{}{}$ over
sets. \jnote{I got rid of the weaker definition, since it seems
  unnatural to me.}\tsnote{Why? It captures things like the Squid
  summary cache -- hash functions are public (in the code, in the
  literature), but you would need to corrupt the HTTP proxy-server to
  get the representation.}
A set $S$ is chosen from this distribution, and a representation
$(M,\pubaux,\privaux)$ of that set is computed.
In one experiment ($\ExpPriv{\Pi,\distr{}{}}$), the attacker is given $M, \pubaux$;
in a second experiment ($\ExpPrivNull{\Pi,\distr{}{}}{}$), it is not.
In both cases, the attacker is given
access to an oracle via which it can
issue queries and obtain the corresponding responses.
For a given $\distr{}{}$ and $A$, we define the advantage measure
$\AdvPriv{\Pi,\distr{}{}}{A} \bydef
\left| \Prob{\ExpPriv{\Pi,\distr{}{}}{A}=1} - \Prob{\ExpPrivNull{\Pi,\distr{}{}}{A}=1} \right|$.
We track the
time-complexity~$t$ and number of oracle queries~$q$ made by the adversary.

@@

\medskip
\experimentv{$\ExpPrivNull{\Pi, \distr{}{}}{A}$} \\
$S \getsr \distr{}{}$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(\emptystring,\emptystring)$\\
if $z \in S$ then return 1\\
return 0\\
%\medskip
%\experimentv{$\ExpWPriv{\setprim,\distr{}{}}{A}$}\\
%$S \getsr \distr{}{}$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
%$z \getsr A^{\TestOracle}(\pubaux)$\\
%if $z \in S$ then Return 1\\
%Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\pubaux,\privaux,q)$\\
return~$a$
}
}
\caption{Experiments for a ``one-wayness'' style privacy
  definition.}
\label{fig:privacy-ow}
\end{figure}

@@

\jnote{Actually, I am unsure whether a one-wayness definition is independently
interesting if we have (and can achieve) a semantic-security definition.}
\tsnote{Depends on what information we decide is okay to leak.  A
  classical BF gives an~$M$ that leaks a good approximation of $|S|$.
Do we want that to be considered semantically secure?  On the other
hand, a classical BF is one-way in the ROM, up to the min-entropy of
the distribution over~$S$.  So that may already give an interesting
example that fits in the gap.}
Our semantic-secure definition is simulation-based (see
Figure~\ref{fig:privacy-ss}).
In this definition we compare the probabilities with which an attacker $A$ outputs~1
in two experiments: one ``real'' and one ``simulated.''
In the real experiment (ss-rep-1), $A$ outputs a set $S$ and is given the
$M,\pubaux$ that result from running $\Rep(S)$.
In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $M, \pubaux$ output
by a simulator $\calS$ that is only given ${\sf leak}(S)$. \jnote{Note
there is no need for a query oracle here, since the attacker knows the set. Interestingly,
if we provide a query oracle in the real world and an oracle that returns the correct
answer in the simulated world, then this definition seems to imply
correctness also.}
\tsnote{Need to pass state between stages if you want~$A$ to know the
  set it previously sampled, right?}
For a given function ${\sf leak}$, adversary $A$, and simulator~$\calS$,
we define the advantage measure
$\AdvPrivSS{\Pi,{\sf leak}}{A,\calS} \bydef
\left| \Prob{\ExpPrivSSreal{\Pi}{A}=1} -
\Prob{\ExpPrivSSsim{\Pi,{\sf leak}}{A, \calS}=1} \right|$.
Informally, a scheme $\Pi$ is secure with respect to some leakage ${\sf leak}$
if there is a simulator $\calS$ such that $\AdvPrivSS{\Pi,{\sf leak}}{A,\calS}$ is small
for all~$A$. Intuitively, this means that the public portion
$M, \pubaux$ of the representation of a set~$S$ leaks only ${\sf leak}(S)$.

@@

\medskip
\experimentv{$\ExpPrivSSsim{\Pi}{A, \calS}$}\\
$S \gets A()$\\
$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$(M',\pubaux) \gets \calS(\pubaux)$ \\
return $A(M',\pubaux)$\\
}
}
\caption{Experiments for a ``semantic-security'' style privacy
  definition.}
\label{fig:privacy-ss}
\end{figure}

>>>>

In this experiment we track the time-complexity (relative to some
implied model of computation) and query-complexity (i.e., number of
queries) of the adversary~$A$.
We define the advantage of adversary~$A$ in the correctness experiment as
$\AdvCorrect{\Pi,\distr{}{},r}{A} = \Prob{\ExpCorrect{\Pi,\distr{}{}, r,}{A}=1}$.
Overloading notation, we write $\AdvCorrect{\Pi,\distr{}{},r}{t,q}$ for the maximum over all~$t$-time adversaries that ask at most~$q$ queries. Roughly, we say that a
set-representation~$\Pi$ is $(t,q,r,\epsilon')$-correct if $\AdvCorrect{\Pi,\distr{}{},r}{t,q} \leq \epsilon'$.
\jnote{Note that test includes err because we don't want to penalize
the adversary's resources for computing $q(S)$.}

@@

\item If a scheme is $(t,q,1,\epsilon)$-correct, then it is also $\epsilon$-secure under the NY definition,
at least for attackers making at most $q-1$ queries.
This is immediate.
\end{enumerate}
\jnote{Case of $r=1$ does not necessarily imply anything for $r>1$: can have a scheme
where finding the first false positive is hard but then the rest are easy; can have
a scheme where finding one false positive is easy but there do not exist
any more false positives.}

@@

\jnote{OK, from here on I specialize to set-representation data structures\ldots}
The one-wayness definition (see
Figure~\ref{fig:privacy-ow}) is parameterized by a distribution $\distr{}{}$ over
sets. \jnote{I got rid of the weaker definition, since it seems
  unnatural to me.}\tsnote{Why? It captures things like the Squid
  summary cache -- hash functions are public (in the code, in the
  literature), but you would need to corrupt the HTTP proxy-server to
  get the representation.} \jnote{We can include the weaker definition, or perhaps
  it is cleaner to just have the syntax output $(\pub, \privaux)$ with $\pub$ always
  public and $\privaux$ always private; a scheme can then choose whether $M$ is in $\pub$
  or $\privaux$. If we do this, then need to be careful how to define size.}
A set $S$ is chosen from this distribution, and a representation
$(M,\pubaux,\privaux)$ of that set is computed.
In one experiment ($\ExpPriv{\Pi,\distr{}{}}$), the attacker is given $M, \pubaux$;
in a second experiment ($\ExpPrivNull{\Pi,\distr{}{}}{}$), it is not.
In both cases, the attacker is given
access to an oracle via which it can
issue queries and obtain the corresponding responses.
For a given $\distr{}{}$ and $A$, we define the advantage measure
$\AdvPriv{\Pi,\distr{}{}}{A} \bydef
\left| \Prob{\ExpPriv{\Pi,\distr{}{}}{A}=1} - \Prob{\ExpPrivNull{\Pi,\distr{}{}}{P}=1} \right|$.
We track the
time-complexity~$t$ and number of oracle queries~$q$ made by the adversary.
\jnote{Change. Compare $A$ in the 1-world to $P$ in the 0-world. Security means
there exists a $P$
such that for all~$A$ the following holds: $A$ in the 1-world does not do much better than
$P$ in the 0-world. Note that there is a canonical $P$ that does best, information-theoretically.}

@@

\medskip
\experimentv{$\ExpPrivNull{\Pi, \distr{}{}}{P}$} \\
$S \getsr \distr{}{}$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr P()$\\
if $z \in S$ then return 1\\
return 0\\
%\medskip
%\experimentv{$\ExpWPriv{\setprim,\distr{}{}}{A}$}\\
%$S \getsr \distr{}{}$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
%$z \getsr A^{\TestOracle}(\pubaux)$\\
%if $z \in S$ then Return 1\\
%Return 0\\
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(M,\pubaux,\privaux,q)$\\
return~$a$
}
}
\caption{Experiments for a ``one-wayness'' style privacy
  definition.}
\label{fig:privacy-ow}
\end{figure}

@@

\jnote{Actually, I am unsure whether a one-wayness definition is independently
interesting if we have (and can achieve) a semantic-security definition.}
\tsnote{Depends on what information we decide is okay to leak.  A
  classical BF gives an~$M$ that leaks a good approximation of $|S|$.
Do we want that to be considered semantically secure?  On the other
hand, a classical BF is one-way in the ROM, up to the min-entropy of
the distribution over~$S$.  So that may already give an interesting
example that fits in the gap.} \jnote{Yes. Semantic security
is parameterized by the leakage function, and so might or might not imply
one-wayness.}
Our semantic-secure definition is simulation-based (see
Figure~\ref{fig:privacy-ss}).
In this definition we compare the probabilities with which an attacker $A$ outputs~1
in two experiments: one ``real'' and one ``simulated.''
In the real experiment (ss-rep-1), $A$ outputs a set $S$ and is given the
$M,\pubaux$ that result from running $\Rep(S)$.
In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $M, \pubaux$ output
by a simulator $\calS$ that is only given ${\sf leak}(S)$. \jnote{${\sf leak}$ can
be randomized.} \jnote{Note
there is no need for a query oracle here, since the attacker knows the set. Interestingly,
if we provide a query oracle in the real world and an oracle that returns the correct
answer in the simulated world, then this definition seems to imply
correctness also.}
\tsnote{Need to pass state between stages if you want~$A$ to know the
  set it previously sampled, right?} \jnote{Yes, unless by convention all algorithms
  are stateful. (smiley face).}
For a given function ${\sf leak}$, adversary $A$, and simulator~$\calS$,
we define the advantage measure
$\AdvPrivSS{\Pi,{\sf leak}}{A,\calS} \bydef
\left| \Prob{\ExpPrivSSreal{\Pi}{A}=1} -
\Prob{\ExpPrivSSsim{\Pi,{\sf leak}}{A, \calS}=1} \right|$.
Informally, a scheme $\Pi$ is secure with respect to some leakage ${\sf leak}$
if there is a simulator $\calS$ such that $\AdvPrivSS{\Pi,{\sf leak}}{A,\calS}$ is small
for all~$A$. Intuitively, this means that the public portion
$M, \pubaux$ of the representation of a set~$S$ leaks only ${\sf leak}(S)$.

@@

%\medskip
%\experimentv{$\ExpPrivSSsim{\Pi}{A, \calS}$}\\
%$S \gets A()$\\
%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
%$(M',\pubaux) \gets \calS(\pubaux)$ \\
%return $A(M',\pubaux)$\\
}
}
\caption{Experiments for a ``semantic-security'' style privacy
  definition.}
\label{fig:privacy-ss}
\end{figure}

### 2016-08-26 results.tex
notes from phone call

\section{Achieving Security Notions}
\heading{Linear-PRF construction. }
Here we consider a set-multiplicity data structure that was attacked by Neidermayer et al. in~\cite{xxx}.  Let $\Pi_{\mathrm{lin}}= (\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ be defined as follows. Fix an $n \geq 0$, let $\mathcal{S}=[\univ]^n$, and let $\Sigma=\Gamma=\bits$. The queries are defined so that $q_x(S)=1$ if $x \in S$, and 0 otherwise.  Fix non-empty sets ~$\calK$, $\univ$ and integers $k,m,n>0$.  Let $F\colon\mathcal{K} \times \univ \to [m]$ be a function family. Define $\Hash$ as an algorithm that samples two keys $K_0,K_1 \getsr \mathcal{K}$ and defines $h_j(x) = F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$ for $j \in [1,k]$.  $\Rep$ uses $\Hash$ to set $\privaux=\pubaux = (h_1, \ldots, h_k)$, computes an $m$ bit array, $M$ in the standard way and returns $(M,\pubaux,\privaux)$.  The $\Qry$ algorithm gets $(M,\privaux, q_x)$ as input, and returns the AND of values at $M[h_1(x)],\ldots,M[h_k(x)]$. It must be noted that $\Pi_{\mathrm{lin}}$ admits errors in form of false-positives(FP) only. So, error rate of $\Pi_{\mathrm{lin}}$ is same as the (non-adaptive) FP rate. The following result shows, informally, that if~$F$ is a good PRF and the error rate is sufficiently small, then $\Pi_\mathrm{lin}$ is correct against adaptive error-finding adversaries. Henceforth, we refer errors and error-rate in $\Pi_{\mathrm{lin}}$ as FP's and FP rate, respectively.

@@

\heading{Correctness. }  Here we give security proofs and attacks with respect to the correctness notions.
\begin{itemize}
\item Show Bloom Filter is correct in the ROM 
\item correctness security/attacks on bigram/PRF-based double-hashing construction ($h_j(x) = F_{K1}(x) + j\cdot F_{K2}(x) \bmod m$ where the~$x$ are bigrams of names, etc.) 
\item correctness-security/attacks on bigram/domain-separated PRF construction ($h_j(x)=F_K(\langle j,x \rangle) \bmod m$, or just assume range of~$F$ is $[m]$.)
\item correctness-security/attacks Dong, Chen, Wen ``garbled Bloom filter'' construction

@@

\item Prove privacy bounds for the constructions from NY

@@

\item Prove a privacy bound for the bigram/PRF-based double-hashing construction that Neidermayer et al.\ attacks. I expect that the provable security bound is considerably worse than the min-entropy because of the way the representation is made.  (Essentially, the Hamming weight of the representation is a good estimate of the length of the longest surname in filter.)

>>>>

\section{Achieving Security Notions}

\jnote{Outline:
}

\heading{Linear-PRF construction. }
Here we consider a set-multiplicity data structure that was attacked by Neidermayer et al. in~\cite{xxx}.  Let $\Pi_{\mathrm{lin}}= (\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ be defined as follows. Fix an $n \geq 0$, let $\mathcal{S}=[\univ]^n$, and let $\Sigma=\Gamma=\bits$. The queries are defined so that $q_x(S)=1$ if $x \in S$, and 0 otherwise.  Fix non-empty sets ~$\calK$, $\univ$ and integers $k,m,n>0$.  Let $F\colon\mathcal{K} \times \univ \to [m]$ be a function family. Define $\Hash$ as an algorithm that samples two keys $K_0,K_1 \getsr \mathcal{K}$ and defines $h_j(x) = F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$ for $j \in [1,k]$.  $\Rep$ uses $\Hash$ to set $\privaux=\pubaux = (h_1, \ldots, h_k)$, computes an $m$ bit array, $M$ in the standard way and returns $(M,\pubaux,\privaux)$.  The $\Qry$ algorithm gets $(M,\privaux, q_x)$ as input, and returns the AND of values at $M[h_1(x)],\ldots,M[h_k(x)]$. It must be noted that $\Pi_{\mathrm{lin}}$ admits errors in form of false-positives(FP) only. So, error rate of $\Pi_{\mathrm{lin}}$ is same as the (non-adaptive) FP rate. The following result shows, informally, that if~$F$ is a good PRF and the error rate is sufficiently small, then $\Pi_\mathrm{lin}$ is correct against adaptive error-finding adversaries. Henceforth, we refer errors and error-rate in $\Pi_{\mathrm{lin}}$ as FP's and FP rate, respectively.

@@

\heading{Correctness. }  Here we give security proofs and attacks with respect to the correctness notions.
\begin{itemize}
\item Show Bloom Filter is correct in the ROM. \jnote{Should follow along the lines
of Theorem~2, but taking into account adversary's oracle queries.}
\item correctness security/attacks on the bigram/PRF-based double-hashing construction ($h_j(x) = F_{K1}(x) + j\cdot F_{K2}(x) \bmod m$ where the~$x$ are bigrams of names, etc.)
\jnote{Done}
\item correctness-security/attacks on the bigram/domain-separated PRF construction ($h_j(x)=F_K(\langle j,x \rangle) \bmod m$, or just assume range of~$F$ is $[m]$.) \jnote{Done}
\item correctness-security/attacks Dong, Chen, Wen ``garbled Bloom filter'' construction

@@

\item Prove privacy bounds for the constructions from NY. \jnote{Is this interesting?}

@@

\item Prove a privacy bound for the bigram/PRF-based double-hashing construction that Neidermayer et al.\ attacks. I expect that the provable security bound is considerably worse than the min-entropy because of the way the representation is made.  (Essentially, the Hamming weight of the representation is a good estimate of the length of the longest surname in filter.)
\jnote{Maybe tailor leakage function appropriately, i.e., so that
it only leaks the number of bigrams?}
